---
title: "Bayesian"
author: "T. Moudiki"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bayesian}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `tisthemachinelearner` package provides a simple R interface to scikit-learn models through Python's `tisthemachinelearner` package. This vignette demonstrates how to use the package with R's built-in `mtcars` dataset.

## Setup

First, let's load the required packages:

```{r}
library(tisthemachinelearner)
library(reticulate)
```

## Data Preparation

We'll use the classic `mtcars` dataset to predict miles per gallon (mpg) based on other car characteristics:

```{r}
# Load data
data(mtcars)
head(mtcars)

# Split features and target
X <- as.matrix(mtcars[, -1])  # all columns except mpg
y <- mtcars[, 1]              # mpg column

# Create train/test split
set.seed(42)
train_idx <- sample(nrow(mtcars), size = floor(0.8 * nrow(mtcars)))
X_train <- X[train_idx, ]
X_test <- X[-train_idx, ]
y_train <- y[train_idx]
y_test <- y[-train_idx]

# R6 interface
model <- Regressor$new(model_name = "BayesianRidge")
start <- proc.time()[3]
model$fit(X_train, y_train)
end <- proc.time()[3]
cat("Time taken:", end - start, "seconds\n")

start <- proc.time()[3]
preds <- model$predict(X_test, method="bayesian")
end <- proc.time()[3]
cat("Time taken:", end - start, "seconds\n")
print(preds)

# S3 interface
start <- proc.time()[3]
model <- regressor(X_train, y_train, model_name = "GaussianProcessRegressor")
end <- proc.time()[3]
cat("Time taken:", end - start, "seconds\n")

start <- proc.time()[3]
preds <- predict(model, X_test, method="bayesian")
end <- proc.time()[3]
cat("Time taken:", end - start, "seconds\n")
print(preds)
```

## Conclusion

This example demonstrates how to:

1. Prepare R data for use with the regressor
2. Fit different types of regression models
3. Make predictions on new data
4. Calculate and compare model performance
5. Visualize results

The `tisthemachinelearner` package makes it easy to use scikit-learn models with R data, combining the familiarity of R data structures with the power of Python's machine learning ecosystem.

## Session Info

```{r}
sessionInfo()
```
